Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-01-09 paper/04-design.tex
changed paper sec: security model

>>>>

\subsection{System and Security Model}

Our security analysis considers the worst case scenario, in which the consumer issues an interest that has not been cached in any of the routers from the consumer nor producer domains. Therefore, the interest must traverse the whole network until reaching the content producer. Conversely, the content needs to be forwarded all the way back though the same path satisfying the routers' PIT entries. A system that is secure in this worst case is also secure when the content has been previously cached in some router along the way.

\textbf{Adversary Goals and Capabilities.} The goal of the adversary is either 1) to retrieve any information associated with the original issued interest $I_p$ and/or the original content $C_p$ or 2) to retrieve the identities of the consumer and/or producer, thus violating the anonymity in the communication. An adversary is also considered successful if it is able to impersonate the content producer by faking a content response. Since the original interest and the original content are visible inside the consumer and producer domains, we here assume that the adversary cannot eavesdrop or compromise hosts inside such domains. It is also worth to emphasize that, by the conceptual design of the VPN, communication is anonymous to hosts from outside the VPN but not to hosts that belong to that VPN. Anyhow, one-to-one anonymous communication is still achievable sing the VPN paradigm if the communication must be anonymous to any other host in the network\footnote{In the case that communication should be anonymous even to nodes inside the consumer and producer domains, $G_c$ and $G_p$ could be ran as processes within the consumer and producer hosts, respectively. This way, packets exchanged between them would remain anonymous to any other node in the network}. This also means that, as components of the producer and consumer domains, we assume that the gateways $G_c$ and $G_p$ cannot be compromised.

In our model the adversary is allowed to perform the following actions (when outside the consumer and producer domains):

\begin{itemize}
	\item \textbf{Observe traffic replay and replace messages:}
	\item \textbf{Deploy compromised routers:}
	\item \textbf{Compromise existing routers:}
	\item \textbf{Deploy compromised caches:}
\end{itemize}

\subsection{Additional Considerations}

\textbf{Gateway-to-Gateway Authentication:}

\textbf{Denial of Service:}
